**The Heart can Lie: A Preliminary Investigation of the Role of Interoception and Theory of Mind in Deception**

### 2024-09-15 paper/manuscript.Rmd
R3

The higher *Focus* interoception score was significantly associated with an increased confidence in truths in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$); a consistent pattern, although non-significant, was found for confidence in truth in the interrogation conditions ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$). The *Focus* interoception score was also positively correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$). No significant association was found with RT for lies and heart rate in both conditions

>>>>

The higher *Focus* interoception score was significantly associated with an increased confidence in truths in the polygraph ($\beta=0.17,~95\%~CI~[-0.01, 0.34],~pd = 97.16\%$); a consistent pattern, although non-significant, was found for confidence in truths in the interrogation condition ($\beta=0.15,~95\%~CI~[-0.02, 0.32],~pd = 95.76\%$). The *Focus* interoception score was also positively correlated with the dispositional lying *Ability* trait ($r = 0.50,~95\%~CI~[0.22, 0.74],~BF_{10} = 34.37\%$). No significant association was found with RT for lies and heart rate in both conditions.
